---
title: "Survey data analysis"
author: "Jackie Ouzman"
date: "22/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(readxl)
library(DT)
#install.packages("scales")
library(scales)
```

#### Do analysis in sections 
first section is question 1 to XXX

Bring in the data and assign the correct headings
```{r import dataset advisor, include=FALSE}

#These names are very long perhaps we can make them shorter?

headers <- read_excel("Using soil and plant testing data to better inform nutrient management.xlsx", 
                   sheet = "Data", col_names=FALSE, range = "A1:DO1")
data <- read_excel("Using soil and plant testing data to better inform nutrient management.xlsx", 
                   sheet = "Data", col_names=FALSE, range = "A4:DO74")

names(data) <- headers
#names(data)


```

#### subset of data

setting the display names and the order I want them to appear

```{r setting up the region names and order, include=FALSE}
data <- mutate(data,
             names_display =case_when(
               Q1_region == "SA - Mallee (low rainfall)" ~  "SA - Mallee",
               Q1_region == "SA – Lower EP (medium rainfall)" ~  "SA – Lower EP",
               Q1_region == "SA - Mid North (medium rainfall)" ~  "SA - Mid North",
               Q1_region == "SA - Yorke Peninsula (medium rainfall)" ~  "SA - Yorke Peninsula",
               Q1_region == "SA - Upper EP (low rainfall)" ~  "SA - Upper EP",
               Q1_region == "SA - South East (medium rainfall)" ~  "SA - South East",
               Q1_region == "VIC - Wimmera (medium rainfall)" ~  "VIC - Wimmera",
               Q1_region == "VIC - Mallee (low rainfall)" ~  "VIC - Mallee",
               Q1_region == "VIC - Southern region (high rainfall)" ~  "VIC - Southern region",
               Q1_region == "Other (please specify)" ~  "Other"))
data <- mutate(data, names_display = fct_relevel(names_display, c("SA - Mallee", 
                                       "SA – Lower EP", 
                                       "SA - Mid North", 
                                       "SA - Yorke Peninsula", 
                                       "SA - Upper EP", 
                                       "SA - South East", 
                                       "VIC - Wimmera",
                                       "VIC - Mallee",
                                       "VIC - Southern region",
                                       "Other")))

```

#### Question 1 
In which argo-elecological region do you work / are your clients based?
This is not done yet

#### **Question 2** 
What is the average total area cropped (hectares) that you have managed for clients over the last 3 seasons?
**Analysed copped area by regions**


```{r Q2 analysis and table, echo=FALSE}

Q2_regions <- group_by(data, names_display) %>% 
  summarise(
    count = n(),
    Ave_Cropped_Area = round(mean(`Q2_Cropped Area`), 0)) %>% 
    arrange(names_display)

#head(Q2_regions,3)

datatable(Q2_regions,  colnames = c( "names", "count", "average cropped area"),
          rownames = FALSE)
          

```
```{r Q2 graph regions, echo=FALSE}
ggplot(Q2_regions, aes(names_display, Ave_Cropped_Area))+
  geom_col()+
  theme_classic()+
  labs(x= "Regions",
       y = "Cropped area",
       title = "Total area cropped (hectares)",
       subtitle = "Agronomist",
       caption = "Q) What is the average total area cropped (hectares) that you have managed for clients over the last 3 seasons?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(labels =  comma)
```

#### Question 3 
Of the land you manage with clients, what percentage would be the following crops, by area? (please enter a whole number without the % sign.
Every row needs a number, so if there is none grown, please enter 0.)

Cerals (wheat, barley, oats)
Canola
Pulses (peas, beans, lupins, lentils, chickpeas)
Pasture
Hay
Fallow

#### Question 4
When thinking about your average client's annual variable costs, what percentage would fertilisers account for?

#### Question 5
What are the main nutrient deficiencies your clients encounter?

#### **Question 6** 
Do you recommend soil and or plant testing?

```{r Q6 summary, echo=FALSE}
#All agronomist  
Q6_all <- data %>% 
  count(Q6_recommend_testing) %>% 
  mutate(percent = 
        (freq = n / sum(n)))
#head(Q6_all)

ggplot(Q6_all, aes(Q6_recommend_testing, percent))+
  geom_col()+
  geom_text(aes(label = percent(signif(percent),1), vjust = "inward", hjust = "inward"))+
  theme_classic()+
  labs(x= "All regions",
       y = "Recommend testing",
       title = "Recommend soil and or plant testing",
       subtitle = "Agronomist",
       caption = "Q) Do you recommend soil and or plant testing?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent)


#agronomist by region

Q6_byRegion <- data %>%
  group_by(names_display, Q6_recommend_testing) %>%
  summarise(n = n()) %>%
    mutate(percent = 
        (freq = n / sum(n)))
   #mutate(percent = round(
  #      (freq = n / sum(n))*100,3)) #having some trouble with the rounding



#head(Q6_byRegion)

ggplot(Q6_byRegion, aes(names_display, percent, fill=Q6_recommend_testing ))+
  geom_col()+
  #geom_text(aes(label = percent(signif(percent),1), vjust = "inward", hjust = "inward"))+
  theme_classic()+
  labs(x= "Regions",
       y = "Recommend testing",
       fill = "",
       title = "Recommend soil and or plant testing",
       subtitle = "Agronomist",
       caption = "Q) Do you recommend soil and or plant testing?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent)

#graph of agronomist advising no
filter(Q6_byRegion, Q6_recommend_testing == "No") %>% 
ggplot(aes(names_display, percent))+
  geom_col()+
  geom_text(aes(label = percent(signif(percent),1), vjust = "inward", hjust = "inward"))+
  theme_classic()+
  labs(x= "Regions",
       y = "Do not recommend testing",
       title = "Recommend soil and or plant testing",
       subtitle = "Agronomist",
       caption = "Q) Do you recommend soil and or plant testing?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent)

```

#### Question 7
Of your clients, how many of them rely entirely on you to make the nutrient decisions?
Of your clients, how many of them rely somewhat on you to make the nutrient decisions?
Of your clients, how many of them make their own nutrient decisions?

#### Question 8
To what extent are you responsible for determining how much testing is done on your clients' farms?

#### Question 9
To what extent do the test results influence your recommendations?

#### Question 10
What are your 3 main sources of information or advice for what nutrients you recommend and at what rate? #Indicate if this is different for N, P and other nutrients
Source 1
Source 2
Source 3

#### Question 11
#### Explain your approach to soil testing P, N and other micronutrients ...
P
N
Micronutrients

#### **Question 12**
#### Can you please provide some specific information on ..
#### What % of your clients soil tested in 2018?
#### What % of your clients tested for N in 2018?
What % of your clients tested for N to at least 60cm in 2018?
#### What % of your clients tested for P in 2018?


```{r Q12 data work up and DT summary, echo=FALSE}
#All agronomist  
#table(data$Q12_percent_testing_2018)
#table(data$Q12_percent_N_testing_2018)
#table(data$Q12_percent_testing_P_2018)
#table(data$Q12_percent_testing_N_60cm_2018)

Q12_percent_testing_2018 <- data %>%
  group_by( Q12_percent_testing_2018 ) %>%
  summarise(n = n()) %>%
  mutate(percent = (freq = n / sum(n)),
         type = "percent_testing_2018")
Q12_percent_testing_2018 <- Q12_percent_testing_2018 %>%
  select(n,
        percent,
        type,
        bins = Q12_percent_testing_2018)

Q12_percent_N_testing_2018 <- data %>%
  group_by(  Q12_percent_N_testing_2018 ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_N_testing_2018")
Q12_percent_N_testing_2018 <- Q12_percent_N_testing_2018 %>%
  select(n,
         percent,
         type,
         bins = Q12_percent_N_testing_2018)

Q12_percent_testing_P_2018 <- data %>%
  group_by(  Q12_percent_testing_P_2018 ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_P_testing_2018")
Q12_percent_testing_P_2018 <- Q12_percent_testing_P_2018 %>%
  select(n,
         percent,
         type,
         bins = Q12_percent_testing_P_2018)

Q12_percent_testing <- rbind(Q12_percent_testing_2018,
                             Q12_percent_N_testing_2018,
                             Q12_percent_testing_P_2018)
Q12_percent_testing <- select(Q12_percent_testing,
                              type,
                              bins,
                              percent, n)      
#head(Q12_percent_testing) 


labels <- c(percent_N_testing_2018 = "N", 
            percent_P_testing_2018 = "P",
            percent_testing_2018 = "testing")


#head(Q12_percent_testing)
Q12_percent_testing_for_table <- mutate(Q12_percent_testing,
                                        percent1 = round(percent*100,2),
                                        label_name = case_when(
                                          type == "percent_N_testing_2018" ~ "N",
                                          type == "percent_P_testing_2018" ~ "P",
                                          type == "percent_testing_2018" ~ "any testing")) %>% 
                                select(label_name, bins, percent1 )

#head(Q12_percent_testing_for_table)


filter(Q12_percent_testing_for_table, bins != "NA") %>% 
  datatable(colnames = c("testing for", "bins", "percentage of tetsing done"))


```

```{r Q12 graphs , echo=FALSE}

caption <- c(
"Q) What % of your clients soil tested in 2018?
Q) What % of your clients tested for N in 2018?
Q) What % of your clients tested for P in 2018?")



filter(Q12_percent_testing, bins != "NA") %>% 
ggplot( aes(bins, percent))+
  geom_col()+
  #geom_text(aes(label = percent(signif(percent),1), vjust = "inward", hjust = "inward"))+
  theme_classic()+
  facet_wrap(. ~ type, labeller=labeller(type = labels)) +  
  labs(x= "bins",
       y = "",
       title = "In 2018 what % of your clients tested...",
       subtitle = "Agronomist",
       caption = caption)+
       theme(axis.text.x=element_text(angle=90,hjust=1),
       plot.caption = element_text(size = 8, hjust = 0))+
       scale_y_continuous(labels = scales::percent)

```

#### Question 13
Which tests do you currently use for soil N testing?
Nitrogen 1 - Type of test
Nitrogen 1 - Frequency (times per season)
Nitrogen 1 - How many representative samples per paddock
Nitrogen 2 - Type of test
Nitrogen 2 - Frequency (times per season)
Nitrogen 2 - How many representative samples per paddock
Nitrogen 3 - Type of test
Nitrogen 3 - Frequency (times per season)
Nitrogen 3 - How many representative samples per paddock
How frequently are paddocks tested i.e. every 3 years, every 5 years ... other?

#### Question 14
Which tests do you use for P tests?
Phosphorus 1 - Type of test
Phosphorus 1 - Frequency (times per season)
Phosphorus 1 - How many representative samples per paddock
Phosphorus 2 - Type of test
Phosphorus 2 - Frequency (times per season)
Phosphorus 2 - How many representative samples per paddock
Phosphorus 3 - Type of test
Phosphorus 3 - Frequency (times per season)
Phosphorus 3 - How many representative samples per paddock
Phosphorus 4 - Type of test
Phosphorus 4 - Frequency (times per season)
Phosphorus 4 - How many representative samples per paddock
Phosphorus 5 - Type of test
Phosphorus 5 - Frequency (times per season)
Phosphorus 5 - How many representative samples per paddock
How frequently are your clients paddocks tested i.e. every 3 years, every 5 years ... other?

#### Question 14
What tests do you use for Potassium testing ...
Potassium 1 - Type of test
Potassium 1 - Frequency (times per season)
Potassium 1 - How many representative samples per paddock
Potassium 2 - Type of test
Potassium 2 - Frequency (times per season)
Potassium 2 - How many representative samples per paddock
Potassium 3 - Type of test
Potassium 3 - Frequency (times per season)
Potassium 3 - How many representative samples per paddock
How frequently are your clients paddocks tested i.e. every 3 years, every 5 years ... other?9

#### Question 14
And, which tests do you use for micronutrients?
1 - Type of test
1 - Frequency (times per season)
1 - How many cores per paddock
2 - Type of test
2 - Frequency (times per season)
2 - How many cores per paddock
3 - Type of test
3 - Frequency (times per season)
3 - How many cores per paddock
4 - Type of test
4 - Frequency (times per season)
4 - How many cores per paddock
5 - Type of test
5 - Frequency (times per season)
5 - How many cores per paddock
6 - Type of test
6 - Frequency (times per season)
6 - How many cores per paddock
7 - Type of test
7 - Frequency (times per season)
7 - How many cores per paddock
8 - Type of test
8 - Frequency (times per season)
8 - How many cores per paddock
How frequently are your clients paddocks tested i.e. every 3 years, every 5 years ... other?10

#### Question 15
What are the top 3 reasons for soil testing on your clients farms ...
1
2
3
#### Question 16
Please indicate why you don't do more SOIL Nitrogen testing:
The cost of soil sampling
The time required for soil sampling
The cost of soil testing lab analysis
The difficulty in being able to represent the variability in a paddock
The level of accuracy of soil testing lab analysis
The ability to translate soil test results into a profitable fertiliser decision for my paddock
Not being able to get soil test results at the right time for decision making
General comments:

```{r Q16 data work up and DT summary, echo=FALSE}
Q16_why_not_moreN_time <- data %>%
  group_by(  Q16_why_not_moreN_time ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q16_why_not_moreN_time") %>% 
  filter( Q16_why_not_moreN_time != "NA") %>% 
  select(percent, type)

Q16_why_not_moreN_lab_cost <- data %>%
  group_by(  Q16_why_not_moreN_lab_cost ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q16_why_not_moreN_lab_cost") %>% 
  filter( Q16_why_not_moreN_lab_cost != "NA") %>% 
  select(percent, type)

Q16_why_not_moreN_lab_accuracy <- data %>%
  group_by(  Q16_why_not_moreN_lab_accuracy ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q16_why_not_moreN_lab_accuracy")%>% 
  filter( Q16_why_not_moreN_lab_accuracy != "NA") %>% 
  select(percent, type)

Q16_why_not_moreN_test_profit_decis <- data %>%
  group_by(  Q16_why_not_moreN_test_profit_decis ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q16_why_not_moreN_test_profit_decis")%>% 
  filter( Q16_why_not_moreN_test_profit_decis != "NA") %>% 
  select(percent, type)

Q16_why_not_moreN_too_slow <- data %>%
  group_by(  Q16_why_not_moreN_too_slow ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q16_why_not_moreN_too_slow")%>% 
  filter( Q16_why_not_moreN_too_slow != "NA") %>% 
  select(percent, type)

Q16_why_not_moreN_variability <- data %>%
  group_by(  Q16_why_not_moreN_variability ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q16_why_not_moreN_variability")%>% 
  filter( Q16_why_not_moreN_variability != "NA") %>% 
  select(percent, type)

Q16_why_not_moreN_cost <- data %>%
  group_by(  Q16_why_not_moreN_cost ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q16_why_not_moreN_cost") %>% 
  filter( Q16_why_not_moreN_cost != "NA") %>% 
  select(percent, type)

Q16_why_not_moreN <- rbind(Q16_why_not_moreN_cost,
                           Q16_why_not_moreN_time,
                           Q16_why_not_moreN_lab_cost,
                           Q16_why_not_moreN_variability,
                           Q16_why_not_moreN_lab_accuracy,
                           Q16_why_not_moreN_test_profit_decis,
                           Q16_why_not_moreN_too_slow)
labels_q16 <- c(Q16_why_not_moreN_cost = "cost", 
                Q16_why_not_moreN_time = "time",
                Q16_why_not_moreN_lab_cost = "cost of lab analysis",
                Q16_why_not_moreN_variability = "vara",
                Q16_why_not_moreN_lab_accuracy = "accuracy of lab analysis",
                Q16_why_not_moreN_test_profit_decis = "translate to profitable decision",
                Q16_why_not_moreN_too_slow = "get results at right time")

Q16_why_not_moreN <- mutate(Q16_why_not_moreN,
                                        percent1 = round(percent*100,2),
                                        label_name = case_when(
                                          type == "Q16_why_not_moreN_cost" ~ "cost",
                                          type == "Q16_why_not_moreN_time" ~ "time",
                                          type == "Q16_why_not_moreN_lab_cost" ~ "cost of lab analysis",
                                          type == "Q16_why_not_moreN_variability" ~ "variability",
                                          type == "Q16_why_not_moreN_lab_accuracy" ~ "accuracy",
                                          type == "Q16_why_not_moreN_test_profit_decis" ~ "translate profitable decision",
                                          type == "Q16_why_not_moreN_too_slow" ~ "get results at right time") ) 

ggplot(Q16_why_not_moreN,  aes(label_name , percent))+
  geom_col()+
  geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "reasons",
       y = "",
       title = "Please indicate why you don't do more SOIL Nitrogen testing:",
       subtitle = "Agronomist",
       caption = "add")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8, hjust = 0))+
  scale_y_continuous(labels = scales::percent)


```


#### Question 17
Please indicate why you don't do more SOIL Phosphorous testing
The cost of soil sampling11
The time required for soil sampling12
The cost of soil testing lab analysis13
The difficulty in being able to represent the variability in a paddock14
The level of accuracy of soil testing lab analysis15
The ability to translate soil test results into a profitable fertiliser decision for my paddock16
Not being able to get soil test results at the right time for decision making17
General comments:18










