---
title: "Survey data analysis"
author: "Jackie Ouzman"
date: "22/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(readxl)
library(DT)
#install.packages("scales")
library(scales)
#install.packages("formattable")
#install.packages("data.table")
library(data.table)
library(formattable)
```

#### General notes 
* 
* Note I have made some adjustment to the heading names in the excel sheet - many questions don't have numbers.

```{r import dataset advisor, include=FALSE}

#These names are very long perhaps we can make them shorter?



headers <- read_excel("Nutrient Management Survey_Agrononomist09092019.xlsx", 
                   sheet = "Data", col_names=FALSE, range = "A1:HL1")
data <- read_excel("Nutrient Management Survey_Agrononomist09092019.xlsx", 
                   sheet = "Data", col_names=FALSE, range = "A5:HL174")
names(data) <- headers
```

* Setting the display names and the order I want them to appear

```{r setting up the region names and order, include=FALSE}

table(data$Q_1)
data <- mutate(data,
             names_display =case_when(
               Q_1 == "SA - Mallee (low rainfall)" ~  "SA - Mallee",
               Q_1 == "SA – Lower EP (medium rainfall)" ~  "SA – Lower EP",
               Q_1 == "SA - Mid North (medium rainfall)" ~  "SA - Mid North",
               Q_1 == "SA - Yorke Peninsula (medium rainfall)" ~  "SA - Yorke Peninsula",
               Q_1 == "SA - Upper EP (low rainfall)" ~  "SA - Upper EP",
               Q_1 == "SA - South East (medium rainfall)" ~  "SA - South East",
               Q_1 == "VIC - Wimmera (medium rainfall)" ~  "VIC - Wimmera",
               Q_1 == "VIC - Mallee (low rainfall)" ~  "VIC - Mallee",
               Q_1 == "VIC - Southern region (high rainfall)" ~  "VIC - Southern region",
               Q_1 == "Other (please specify)" ~  "Other"))


data <- mutate(data, names_display = fct_relevel(names_display, c("SA - Mallee", 
                                       "SA – Lower EP", 
                                       "SA - Mid North", 
                                       "SA - Yorke Peninsula", 
                                       "SA - Upper EP", 
                                       "SA - South East", 
                                       "VIC - Wimmera",
                                       "VIC - Mallee",
                                       "VIC - Southern region",
                                       "Other")))

```



#### **The first series of questions looks at your current farming practices.**

#### **Question 1** 
Agronomist) In which argo-ecological region do you work / are your clients based?

Grower) In which agro-ecological region do you farm


```{r Q1 analysis and table, echo=FALSE}
#both agro and growers
Q1_resp_percent <- data %>% 
  count(Resp_Group) %>% 
  mutate(percent = 
           (freq = n / sum(n)))
#table
#print(Q1_resp_percent)
####graph
ggplot(Q1_resp_percent, aes(Resp_Group, percent ))+
  geom_col()+
  #geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "Regions",
       y = "Respondants",
       fill = "",
       title = "",
       subtitle = "Agronomist and Growers",
       caption = "")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent)    
 
```

```{r Q1_by agro analysis and table, echo=FALSE}

#split into agro and growers
Q1_agro_region_perc <- filter(data, Resp_Group == "Agronomist") %>% 
  count( names_display) %>% 
  mutate(percent = round(
           (freq = n / sum(n)),2))

#table
#print(Q1_agro_region_perc)
#formattable(Q1_agro_region_perc)
datatable(Q1_agro_region_perc, colnames = c( "regions", "count", "percentage"), caption = "Respondents per region - Agronomist")
#graph
ggplot(Q1_agro_region_perc, aes(names_display, percent ))+
  geom_col()+
  #geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "Regions",
       y = "Respondants",
       fill = "",
       title = "",
       subtitle = "Agronomist per region",
       caption = "")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent)    

```


```{r Q2_by growers analysis and table, echo=FALSE}

#split into agro and growers
Q1_grower_region_perc <- filter(data, Resp_Group == "Grower") %>% 
  count( names_display) %>% 
  mutate(percent = round( 
           (freq = n / sum(n)),2))

#table
#print(Q1_grower_region_perc)
datatable(Q1_grower_region_perc, colnames = c( "regions", "count", "percentage"), caption = "Respondents per region - Grower")
#graph growers per region
ggplot(Q1_grower_region_perc, aes(names_display, percent ))+
  geom_col()+
  #geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "Regions",
       y = "Respondants",
       fill = "",
       title = "",
       subtitle = "Growers per region",
       caption = "")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent)    

```

#### **Question 2** 
What is the average total area cropped (hectares) that you have managed for clients over the last 3 seasons?

**Analysed by regions, should we do by cropped area too?**


```{r Q2 analysis and table, echo=FALSE}

Q2_regions <- group_by(data, names_display) %>% 
  summarise(
    count = n(),
    Ave_Cropped_Area = round(mean(`Q_2`), 0)) %>% 
    arrange(names_display)

#head(Q2_regions,3)

datatable(Q2_regions,  colnames = c( "names", "count", "average cropped area"), caption = "Cropped area per region - Argonomist and Grower",
          rownames = FALSE)
          

```
```{r Q2 graph regions, echo=FALSE}
ggplot(Q2_regions, aes(names_display, Ave_Cropped_Area))+
  geom_col()+
  #geom_text(aes(label = Ave_Cropped_Area), vjust = -1.0, hjust = 0.5)+
  theme_classic()+
  labs(x= "Regions",
       y = "Cropped area",
       title = "Total area cropped (hectares)",
       subtitle = "Agronomist and grower",
       caption = "Q)  What is your average total area cropped (hectares, including lease etc) over the last 3 seasons?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(labels =  comma)
```



```{r Q2 graph regions agro only, echo=FALSE}
#head(data)

Q2_regions_agro_grower <- group_by(data, names_display, Resp_Group) %>% 
  summarise(
    count = n(),
    Ave_Cropped_Area = round(mean(`Q_2`), 0)) %>% 
    arrange(names_display)

#head(Q2_regions_agro_grower)

ggplot(Q2_regions_agro_grower, aes(names_display, Ave_Cropped_Area))+
  geom_col()+
  #geom_text(aes(label = Ave_Cropped_Area), vjust = -1.0, hjust = 0.5)+
  facet_wrap(.~ Resp_Group)+
  theme_classic()+
  labs(x= "Regions",
       y = "Cropped area",
       title = "Total area cropped (hectares)",
       subtitle = "Agronomist and grower",
       caption = "Q)  What is your average total area cropped (hectares, including lease etc) over the last 3 seasons?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(labels =  comma)
```


#### **Question 3** 

Which of the following crops do you grow - percentage by area?
 

(please enter a whole number without the % sign.
Every row needs a number, so if there is none grown, please enter 0.)

3.1 Cereals (wheat, barley, oats)

3.2 Canola

3.3 Pulses (peas, beans, lupins, lentils, chickpeas)

3.4 Pasture

3.5 Hay

3.6 Fallow

```{r Q3 graph regions agro only, echo=FALSE}
#head(data)


Q3_regions_agro_grower <- group_by(data, names_display, Resp_Group) %>% 
  summarise(
    Ave_Percent_ceral = round(mean(`Q_3.1`), 0),
    Ave_Percent_canola = round(mean(`Q_3.2`), 0),
    Ave_Percent_pulse = round(mean(`Q_3.3`), 0),
    Ave_Percent_pasture = round(mean(`Q_3.4`), 0),
    Ave_Percent_hay = round(mean(`Q_3.5`), 0),
    Ave_Percent_fallow = round(mean(`Q_3.6`), 0)
    )
    


#head(Q3_regions_agro_grower)
Q3_regions_agro_grower_narrow <- gather(Q3_regions_agro_grower, key = "crop", value = "ave_area",Ave_Percent_ceral:Ave_Percent_fallow )

filter(Q3_regions_agro_grower_narrow, Resp_Group == "Agronomist" ) %>% 
ggplot( aes(names_display, ave_area))+
  geom_col()+
  #geom_text(aes(label = Ave_Cropped_Area), vjust = -1.0, hjust = 0.5)+
  facet_wrap(.~ crop)+
  theme_classic()+
  labs(x= "Regions",
       y = "Crops percent area",
       title = "Avearge percent area by crop",
       subtitle = "Agronomist",
       caption = "Q)  Which of the following crops do you grow - percentage by area?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(labels =  comma)

filter(Q3_regions_agro_grower_narrow, Resp_Group == "Grower" ) %>% 
ggplot( aes(names_display, ave_area))+
  geom_col()+
  #geom_text(aes(label = Ave_Cropped_Area), vjust = -1.0, hjust = 0.5)+
  facet_wrap(.~ crop)+
  theme_classic()+
  labs(x= "Regions",
       y = "Crops percent area",
       title = "Avearge percent area by crop",
       subtitle = "Agronomist",
       caption = "Q)  Which of the following crops do you grow - percentage by area?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(labels =  comma)
```


#### **Question 4**

Agro) When thinking about your average client's annual variable costs, what percentage would fertilisers account for?

Grower) Of your total annual variable costs, what percentage would fertilisers account for?



```{r Q4 graph regions agro only, echo=FALSE}
#head(data)
#table(data$Q_4)
##Looks like an error with data entry'greater than 35% and greater than 35% should be the same


data <- mutate(data,
             Q_4 =case_when(
               Q_4 == "'greater than 35%" ~  "greater than 35%",
               Q_4 == "greater than 35%" ~  "greater than 35%",
               TRUE ~ Q_4))
               
#table(data$Q_4)

data <- mutate(data, Q_4 = fct_relevel(Q_4, c("0-5%", 
                                       "10-15%", 
                                       "15-20%", 
                                       "20-25%", 
                                       "30-35%", 
                                       "greater than 35%", 
                                       "Unsure")))
Q4_resp_percent <- data %>% 
  count(Q_4) %>% 
  mutate(percent = round(
           (freq = n / sum(n)),2))
#Q4_resp_percent


ggplot(Q4_resp_percent, aes(Q_4, percent))+
  geom_col()+
  theme_classic()+
  labs(x= "of total varaible cost",
       y = "Crops percent area",
       title = "Avearge percent area by grouping",
       subtitle = "Agronomist and grower",
       caption = "Q)  Of your total annual variable costs, what percentage would fertilisers account for?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(labels =  comma)

```

#### **Question 5**
What are the main nutrient deficiencies your clients encounter?
What are the main nutrient deficiencies on your farm?


#### **Question 6** 
Do you recommend soil and or plant testing?
Do you do soil and/or plant testing on your farm?


```{r Q6 agro summary agro and grower, echo=FALSE}

Q6_all_agro <- filter(data, Resp_Group == "Agronomist") %>% 
  count(Q_6) %>% 
  mutate(percent = 
        (freq = n / sum(n)))
#head(Q6_all_agro)

ggplot(Q6_all_agro, aes(Q_6, percent))+
  geom_col()+
  geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "All regions",
       y = "Recommend testing",
       title = "Recommend soil and or plant testing",
       subtitle = "Agronomist",
       caption = "Q) Do you recommend soil and or plant testing?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent, limits=c(0, 1.1))
```


```{r Q6 agro summary agro, echo=FALSE}
#agronomist by region

Q6_by_Agro_Region <- filter(data, Resp_Group == "Agronomist") %>% 
  group_by(names_display, Q_6) %>%
  summarise(n = n()) %>%
    mutate(percent = 
        (freq = n / sum(n)))
  
#head(Q6_by_Agro_Region)

ggplot(Q6_by_Agro_Region, aes(names_display, percent, fill=Q_6 ))+
  geom_col()+
  #geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "Regions",
       y = "Recommend testing",
       fill = "",
       title = "Recommend soil and or plant testing",
       subtitle = "Agronomist",
       caption = "Q) Do you recommend soil and or plant testing?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent)

```


```{r Q6 agro summary grower, echo=FALSE}
#grower by region

Q6_by_grower_Region <- filter(data, Resp_Group == "Grower") %>% 
  group_by(names_display, Q_6) %>%
  summarise(n = n()) %>%
    mutate(percent = 
        (freq = n / sum(n)))
  
#head(Q6_by_grower_Region)

ggplot(Q6_by_grower_Region, aes(names_display, percent, fill=Q_6 ))+
  geom_col()+
  #geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "Regions",
       y = "soil / plant testing",
       fill = "",
       title = "Do soil and or plant testing",
       subtitle = "Grower",
       caption = "Q) Do you do soil and/or plant testing on your farm?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent)

```

```{r Q6 agro summary agronomist saying no, echo=FALSE}
#graph of agronomist advising no
#head(Q6_by_Agro_Region)
filter(Q6_by_Agro_Region, Q_6 == "No") %>% 
ggplot(aes(names_display, percent))+
  geom_col()+
  geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "Regions",
       y = "Do not recommend testing",
       title = "Not recommending soil and or plant testing",
       subtitle = "Agronomist",
       caption = "Q) Do you recommend soil and or plant testing?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) + 
  scale_y_continuous(labels = scales::percent, limits=c(0, 0.2))

```

```{r Q6 agro summary grower saying no, echo=FALSE}
#graph of growers not testing
#head(Q6_by_grower_Region)

filter(Q6_by_grower_Region, Q_6 == "No") %>% 
ggplot(aes(names_display,percent ))+
geom_col()+
geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
theme_classic()+
  labs(x= "Regions",
       y = "No testing",
       title = "Not soil and or plant testing",
       subtitle = "Grower",
       caption = "Q) Do you do soil and/or plant testing on your farm?")+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(labels = scales::percent, limits=c(0, 0.8))



```


# **Decision making**


#### **Question 7**

Grower
Who makes the nutrient decisions on your farm?
* self
* Agronomist
* Combination of agronomist and self
* Other
* Other (please specify)


#### **Question 8**

Agronomist
* Of your clients, how many of them rely entirely on you to make the nutrient decisions?
* Of your clients, how many of them rely somewhat on you to make the nutrient decisions?
* Of your clients, how many of them make their own nutrient decisions?




#### **Question 8**
Agronomist
To what extent are you responsible for determining how much testing is done on your clients' farms?
Grower
To what extent does your agronomist determine how much testing is done on your farm? (i.e. % of decision made by your agronomist)


#### **Question 9**
Agronmist
To what extent are you responsible for determining how much testing is done on your clients' farms?
Grower
To what extent does your agronomist determine how much testing is done on your farm? (i.e. % of decision made by your agronomist)

#### **Question 10** 
Note the script and the data base supplied dont match here??
I think I have an out of date script
Agronmist
To what extent does your agronomist make recommendations based on the test results from your farm?
Grower
To what extent do the test results influence your recommendations?

#### **Question 11**
Agronmist
What are your 3 main sources of information or advice for what nutrients you recommend and at what rate? 

Indicate if this is different for N, P and other nutrients

* Source 1
* Source 2
* Source 3

Grower
What are your 3 main sources of information or advice for what nutrients you apply and at what rate? 

Indicate if this is different for N, P and other nutrients

* Source 1
* Source 2
* Source 3


# **Soil testing** 
This section explores how you use soil testing. If you have NOT done soil testing, please go to page  8.

#### **Question 12**

Grower
Explain your approach to soil testing P, N and other micronutrients ...

* P
* N
* Micronutrients

#### **Question 13**
Agronomist
Can you please provide some specific information on ..

* What % of your clients soil tested in 2018? (any testing)
* What % of your clients tested for N in 2018? (N)
* What % of your clients tested for N to at least 60cm in 2018?
* What % of your clients tested for P in 2018? (P)

Note for this question agronomist were asked to nominate the bin.

* 0
* 10-15%
* 15-20%
* 5-10%
* 50 -100%

Grower
Can you please provide some specific information on ..

* What % of  your cropped land was soil tested in 2018 (any testing)
* What % of your cropped land was tested for N in 2018? (N)
* What % of your cropped land was tested for N to at least 60cm in 2018?
* What % of your cropped land was tested for P in 2018? (P)

Note for this question agronomist were asked to nominate the bin.

* 0
* 10-15%
* 15-20%
* 5-10%
* 50 -100%

Note the data set has NA these are not displayed in the graphs
But they have been included in the analysis for the counts.

```{r Q12 data work up and DT summary, echo=FALSE}

data_agro <- filter(data, Resp_Group == "Agronomist" )
data_grower <- filter(data, Resp_Group == "Grower" )

### any test do argo and grower sep and then join

Q13_percent_testing_2018_agro <- data_agro %>%
  group_by( Q_13.1 ) %>%
  summarise(n = n()) %>%
  mutate(percent = (freq = n / sum(n)),
         type = "percent_testing_2018",
         Resp_Group = "Agronomist")
Q13_percent_testing_2018_agro <- Q13_percent_testing_2018_agro %>%
  select(n,
        percent,
        type,
        bins = Q_13.1,
        Resp_Group)

Q13_percent_testing_2018_grower <- data_grower %>%
  group_by( Q_13.1 ) %>%
  summarise(n = n()) %>%
  mutate(percent = (freq = n / sum(n)),
         type = "percent_testing_2018",
         Resp_Group = "Grower")
Q13_percent_testing_2018_grower <- Q13_percent_testing_2018_grower %>%
  select(n,
        percent,
        type,
        bins = Q_13.1,
        Resp_Group)

Q13_percent_testing_2018 <- rbind(Q13_percent_testing_2018_agro, Q13_percent_testing_2018_grower)
#tail(Q13_percent_testing_2018)

#####  N test do agro and grower sep and then join

Q13_percent_N_testing_2018_argo <- data_agro %>%
  group_by(  Q_13.2  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_N_testing_2018",
         Resp_Group = "Agronomist")
Q13_percent_N_testing_2018_argo <- Q13_percent_N_testing_2018_argo %>%
  select(n,
         percent,
         type,
         bins = Q_13.2,
         Resp_Group)
Q13_percent_N_testing_2018_grower <- data_grower %>%
  group_by(  Q_13.2  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_N_testing_2018",
         Resp_Group = "Grower")
Q13_percent_N_testing_2018_grower <- Q13_percent_N_testing_2018_grower %>%
  select(n,
         percent,
         type,
         bins = Q_13.2,
         Resp_Group)

Q13_percent_N_testing_2018 <- rbind(Q13_percent_N_testing_2018_argo, Q13_percent_N_testing_2018_grower)
#tail(Q13_percent_N_testing_2018)


#### P test do agro and grower sep and then join (sorry its messy!)
Q13_percent_P_testing_2018_argo <- data_agro %>%
  group_by(Q_13.4) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_P_testing_2018",
         Resp_Group = "Agronomist")
Q13_percent_P_testing_2018_argo <- Q13_percent_P_testing_2018_argo %>%
  select(n,
         percent,
         type,
         bins = Q_13.4,
         Resp_Group)
temp <- rbind(Q13_percent_testing_2018,
              Q13_percent_N_testing_2018)

temp <- rbind(temp,
              Q13_percent_P_testing_2018_argo)


Q13_percent_P_testing_2018_grower <- data_grower %>%
  group_by(  Q_13.4  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_P_testing_2018",
         Resp_Group = "Grower")
Q13_percent_P_testing_2018_grower <- Q13_percent_P_testing_2018_grower %>%
  select(n,
         percent,
         type,
         bins = Q_13.4,
         Resp_Group)

head(Q13_percent_P_testing_2018_grower)

Q13_percent_testing <- rbind(temp,
              Q13_percent_P_testing_2018_grower)


#print(Q13_percent_testing)

Q13_percent_testing <- select(Q13_percent_testing,
                              type,
                              bins,
                              percent, n, Resp_Group)      
#head(Q13_percent_testing) 


labels <- c(percent_N_testing_2018 = "N", 
            percent_P_testing_2018 = "P",
            percent_testing_2018 = "testing")


#head(Q12_percent_testing)
Q13_percent_testing_for_table <- mutate(Q13_percent_testing,
                                        percent1 = round(percent*100,2),
                                        label_name = case_when(
                                          type == "percent_N_testing_2018" ~ "N",
                                          type == "percent_P_testing_2018" ~ "P",
                                          type == "percent_testing_2018" ~ "any testing")) %>% 
                                select(label_name, bins, percent1, Resp_Group )

#head(Q13_percent_testing_for_table)


filter(Q13_percent_testing_for_table, bins != "NA") %>% 
  datatable(colnames = c("testing for", "bins", "percentage of testing done", "Resp_Group" ))


```

```{r Q13 graphs , echo=FALSE}

caption_agro <- c(
"Q) What % of your clients soil tested in 2018?
Q) What % of your clients tested for N in 2018?
Q) What % of your clients tested for P in 2018?")

caption_grower <- c(
"Q) What % of  your cropped land was soil tested in 2018?
Q) What % of your cropped land was tested for N in 2018?
Q) What % of your cropped land was tested for P in 2018?")


#get the correct order for my labeles
 Q13_percent_testing <- mutate(Q13_percent_testing,
                                bin_as_factors = case_when(
                                  bins == "0" ~ 0,
                                  bins == "5-10%" ~ 5,
                                  bins == "10-15%" ~ 10,
                                  bins == "15-20%" ~ 15,
                                  bins == "20-50%" ~ 20,
                                  bins == "50-100%" ~ 50
                                ))
  Q13_percent_testing$bin_as_factors <- factor(Q13_percent_testing$bin_as_factors,
                                        levels=c(0,5,10,15,20,50),
                                        labels=c("0","5-10%","10-15%","15-20%", "20-50%", "50-100%")) 
  datatable(Q13_percent_testing)
  filter(Q13_percent_testing, bin_as_factors != "NA" &
           Resp_Group == "Agronomist") %>% 
    ggplot( aes(bin_as_factors, percent))+
    geom_col()+
    #geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
    theme_classic()+
    facet_wrap(. ~ type, labeller=labeller(type = labels)) +  
    labs(x= "bins",
         y = "",
         title = "In 2018 what % of your clients tested...",
         subtitle = "Agronomist",
         caption = caption_agro)+
    theme(axis.text.x=element_text(angle=90,hjust=1),
          plot.caption = element_text(size = 8, hjust = 0))+
    scale_y_continuous(labels = scales::percent)

  
  
  filter(Q13_percent_testing, bin_as_factors != "NA" &
           Resp_Group == "Grower") %>% 
    ggplot( aes(bin_as_factors, percent))+
    geom_col()+
    #geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
    theme_classic()+
    facet_wrap(. ~ type, labeller=labeller(type = labels)) +  
    labs(x= "bins",
         y = "",
         title = "In 2018 what % of your cropped land was tested...",
         subtitle = "Grower",
         caption = caption_grower)+
    theme(axis.text.x=element_text(angle=90,hjust=1),
          plot.caption = element_text(size = 8, hjust = 0))+
    scale_y_continuous(labels = scales::percent)
```

Try to take out the percenatge of percentage graph

Can try:

* Agronomists with more than half of clients soil testing in 2018 
* Agronomists with less than 20% of clients  soil testing in 2018 
* Agronomists with no clients soil testing in 2018

* Growers with more than half of clients soil testing in 2018 
* Growers with less than 20% of clients  soil testing in 2018 
* Growers with no clients soil testing in 2018

```{r Q13 graphs other options , echo=FALSE}



subset_soil_testQ_13 <- select(data, Resp_Group, Q_13.1, Q_13.2, Q_13.4)

#Recode to only have 50% or more

#table(subset_soil_testQ_13)
subset_soil_testQ_13 <- mutate(subset_soil_testQ_13,
                              recode_13.1 = case_when(
                                Q_13.1 == "50-100%" ~ "more than half",
                                #Q_13.1 == "0" ~ "less than 20%",
                                Q_13.1 == "10-15%" ~ "less than 20%",
                                Q_13.1 == "15-20%" ~ "less than 20%",
                                Q_13.1 == "0" ~ "Zero"
                                ))

subset_soil_testQ_13 <- mutate(subset_soil_testQ_13,
                               recode_13.2 = case_when(
                                 Q_13.2 == "50-100%" ~ "more than half",
                                 #Q_13.2 == "0" ~ "less than 20%",
                                 Q_13.2 == "10-15%" ~ "less than 20%",
                                 Q_13.2 == "15-20%" ~ "less than 20%",
                                 Q_13.2 == "0" ~ "Zero"
                               ))

subset_soil_testQ_13 <- mutate(subset_soil_testQ_13,
                               recode_13.4 = case_when(
                                 Q_13.4 == "50-100%" ~ "more than half",
                                 #Q_13.4 == "0" ~ "less than 20%",
                                 Q_13.4 == "10-15%" ~ "less than 20%",
                                 Q_13.4 == "15-20%" ~ "less than 20%",
                                 Q_13.4 == "0" ~ "Zero"
                               ))
#head(subset_soil_testQ_13)
subset_soil_testQ_13_agro <- filter(subset_soil_testQ_13, Resp_Group == "Agronomist" )
subset_soil_testQ_13_grower <- filter(subset_soil_testQ_13, Resp_Group == "Grower" )

#any test agro and grower sep and then join
subset_soil_testQ_13_agro_test <- filter(subset_soil_testQ_13_agro, recode_13.1 != "NA") %>%  
  group_by(   recode_13.1  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_testing_2018",
         Resp_Group = "Agronomist")
subset_soil_testQ_13_agro_test <- subset_soil_testQ_13_agro_test %>%
  select(n,
         percent,
         type,
         bins = recode_13.1,
         Resp_Group)

subset_soil_testQ_13_grower_test <- filter(subset_soil_testQ_13_grower, recode_13.1 != "NA") %>%  
  group_by(   recode_13.1  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_testing_2018",
         Resp_Group = "Grower")
subset_soil_testQ_13_grower_test <- subset_soil_testQ_13_grower_test %>%
  select(n,
         percent,
         type,
         bins = recode_13.1,
         Resp_Group)

subset_soil_testQ_13_test <- rbind(subset_soil_testQ_13_grower_test, subset_soil_testQ_13_agro_test)


#N test agro and grower sep and then join
subset_soil_NQ_13_agro_test <- filter(subset_soil_testQ_13_agro, recode_13.2 != "NA") %>%  
  group_by(   recode_13.2  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_N_testing_2018",
         Resp_Group = "Agronomist")
subset_soil_NQ_13_agro_test <- subset_soil_NQ_13_agro_test %>%
  select(n,
         percent,
         type,
         bins = recode_13.2,
         Resp_Group)

subset_soil_testNQ_13_grower_test <- filter(subset_soil_testQ_13_grower, recode_13.2 != "NA") %>%  
  group_by(   recode_13.2  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_N_testing_2018",
         Resp_Group = "Grower")
subset_soil_testNQ_13_grower_test <- subset_soil_testNQ_13_grower_test %>%
  select(n,
         percent,
         type,
         bins = recode_13.2,
         Resp_Group)

subset_soil_N_testQ_13_test <- rbind(subset_soil_testNQ_13_grower_test, subset_soil_NQ_13_agro_test)


#P test agro and grower sep and then join
subset_soil_PQ_13_agro_test <- filter(subset_soil_testQ_13_agro, recode_13.4 != "NA") %>%  
  group_by(   recode_13.4  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_P_testing_2018",
         Resp_Group = "Agronomist")
subset_soil_PQ_13_agro_test <- subset_soil_PQ_13_agro_test %>%
  select(n,
         percent,
         type,
         bins = recode_13.4,
         Resp_Group)

subset_soil_testPQ_13_grower_test <- filter(subset_soil_testQ_13_grower, recode_13.4 != "NA") %>%  
  group_by(   recode_13.4  ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "percent_P_testing_2018",
         Resp_Group = "Grower")
subset_soil_testPQ_13_grower_test <- subset_soil_testPQ_13_grower_test %>%
  select(n,
         percent,
         type,
         bins = recode_13.4,
         Resp_Group)

subset_soil_P_testQ_13_test <- rbind(subset_soil_testPQ_13_grower_test, subset_soil_PQ_13_agro_test)

# get the format I am after I need to make each data frame wide and then join togther
subset_soil_testQ_13_test_wide <- spread(subset_soil_testQ_13_test, key = type, value = percent) %>% mutate(id= paste0(Resp_Group, "_", bins))
subset_soil_N_testQ_13_test_wide <- spread(subset_soil_N_testQ_13_test, key = type, value = percent)%>% mutate(id= paste0(Resp_Group, "_", bins))
subset_soil_P_testQ_13_test_wide <- spread(subset_soil_P_testQ_13_test, key = type, value = percent)%>% mutate(id= paste0(Resp_Group, "_", bins))


subset_soil_N_P_Any_Q_13_wide <- left_join(subset_soil_testQ_13_test_wide, 
                                           subset_soil_N_testQ_13_test_wide,
                                           subset_soil_P_testQ_13_test_wide,
                                           by = "id")


subset_soil_N_P_Any_Q_13_wide <-  subset_soil_testQ_13_test_wide %>%
                                  left_join(subset_soil_N_testQ_13_test_wide, by='id') %>%
                                  left_join(subset_soil_P_testQ_13_test_wide, by='id')

#print(subset_soil_N_P_Any_Q_13_wide$percent_P_testing_2018)
subset_soil_N_P_Any_Q_13_wide <- select( subset_soil_N_P_Any_Q_13_wide,
                                         bins = bins.x,
                                         Resp_Group = Resp_Group.x,
                                         percent_testing_2018,
                                         percent_N_testing_2018,
                                         percent_P_testing_2018)

subset_soil_N_P_Any_Q_13_wide <- mutate_if(subset_soil_N_P_Any_Q_13_wide,
                                           is.double, round,2)

datatable(subset_soil_N_P_Any_Q_13_wide) %>% 
  formatPercentage(c("percent_testing_2018", "percent_N_testing_2018", "percent_P_testing_2018"))

```
#### **Question 14 N**
Grower
Which tests do you currently use for soil N testing?

* Nitrogen 1 - Type of test
* Nitrogen 1 - Frequency (times per season)
* Nitrogen 1 - How many representative samples per paddock
* Nitrogen 2 - Type of test
* Nitrogen 2 - Frequency (times per season)
* Nitrogen 2 - How many representative samples per paddock
* Nitrogen 3 - Type of test
* Nitrogen 3 - Frequency (times per season)
* Nitrogen 3 - How many representative samples per paddock
* How frequently are paddocks tested i.e. every 3 years, every 5 years ... other?

#### **Question 15 P**
grower
Which tests do you use for P tests?

* Phosphorus 1 - Type of test
* Phosphorus 1 - Frequency (times per season)
* Phosphorus 1 - How many representative samples per paddock
* Phosphorus 2 - Type of test
* Phosphorus 2 - Frequency (times per season)
* Phosphorus 2 - How many representative samples per paddock
* Phosphorus 3 - Type of test
* Phosphorus 3 - Frequency (times per season)
* Phosphorus 3 - How many representative samples per paddock
* Phosphorus 4 - Type of test
* Phosphorus 4 - Frequency (times per season)
* Phosphorus 4 - How many representative samples per paddock
* Phosphorus 5 - Type of test
* Phosphorus 5 - Frequency (times per season)
* Phosphorus 5 - How many representative samples per paddock
* How frequently are your clients paddocks tested i.e. every 3 years, every 5 years ... other?

#### **Question 16 Potassium**
What tests do you use for Potassium testing ...

* Potassium 1 - Type of test
* Potassium 1 - Frequency (times per season)
* Potassium 1 - How many representative samples per paddock
* Potassium 2 - Type of test
* Potassium 2 - Frequency (times per season)
* Potassium 2 - How many representative samples per paddock
* Potassium 3 - Type of test
* Potassium 3 - Frequency (times per season)
* Potassium 3 - How many representative samples per paddock
* How frequently are your clients paddocks tested i.e. every 3 years, every 5 years ... other?9

#### **Question 17 micronutrients**
And, which tests do you use for micronutrients?

* 1 - Type of test
* 1 - Frequency (times per season)
* 1 - How many cores per paddock
* 2 - Type of test
* 2 - Frequency (times per season)
* 2 - How many cores per paddock
* 3 - Type of test
* 3 - Frequency (times per season)
* 3 - How many cores per paddock
* 4 - Type of test
* 4 - Frequency (times per season)
* 4 - How many cores per paddock
* 5 - Type of test
* 5 - Frequency (times per season)
* 5 - How many cores per paddock
* 6 - Type of test
* 6 - Frequency (times per season)
* 6 - How many cores per paddock
* 7 - Type of test
* 7 - Frequency (times per season)
* 7 - How many cores per paddock
* 8 - Type of test
* 8 - Frequency (times per season)
* 8 - How many cores per paddock
* How frequently are your clients paddocks tested i.e. every 3 years, every 5 years ... other?10

#### **Question 18**
What are the top 3 reasons for soil testing on your clients farms ...

* 1
* 2
* 3

#### **Question 19**
Please indicate why you don't do more SOIL Nitrogen testing:

* The cost of soil sampling
* The time required for soil sampling
* The cost of soil testing lab analysis
* The difficulty in being able to represent the variability in a paddock
* The level of accuracy of soil testing lab analysis
* The ability to translate soil test results into a profitable fertiliser decision for my paddock
* Not being able to get soil test results at the right time for decision making
* General comments:

```{r Q19 for agro and grower data work up and DT summary, echo=FALSE}

Q19_why_not_moreN_cost <- data %>%
  group_by(  Q_19.1 ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q19_why_not_moreN_cost") %>% 
  filter( Q_19.1 != "NA") %>% 
  select(percent, type)


Q19_why_not_moreN_time <- data %>%
  group_by(  Q_19.2) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q19_why_not_moreN_time") %>% 
  filter( Q_19.2 != "NA") %>% 
  select(percent, type)

Q19_why_not_moreN_lab_cost <- data %>%
  group_by(  Q_19.3 ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q19_why_not_moreN_lab_cost") %>% 
  filter( Q_19.3 != "NA") %>% 
  select(percent, type)

Q19_why_not_moreN_variability <- data %>%
  group_by(  Q_19.4 ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q19_why_not_moreN_variability")%>% 
  filter( Q_19.4 != "NA") %>% 
  select(percent, type)


Q19_why_not_moreN_lab_accuracy <- data %>%
  group_by(  Q_19.5 ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q19_why_not_moreN_lab_accuracy")%>% 
  filter( Q_19.5 != "NA") %>% 
  select(percent, type)


Q19_why_not_moreN_test_profit_decis <- data %>%
  group_by(  Q_19.6 ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q19_why_not_moreN_test_profit_decis")%>% 
  filter( Q_19.6 != "NA") %>% 
  select(percent, type)

Q19_why_not_moreN_too_slow <- data %>%
  group_by(  Q_19.7 ) %>%
  summarise(n = n()) %>%
  mutate(percent =(freq = n / sum(n)),
         type = "Q19_why_not_moreN_too_slow")%>% 
  filter( Q_19.7 != "NA") %>% 
  select(percent, type)




#merge all my dataframes into one
Q19_why_not_moreN <- rbind(Q19_why_not_moreN_cost,
                           Q19_why_not_moreN_time,
                           Q19_why_not_moreN_lab_cost,
                           Q19_why_not_moreN_variability,
                           Q19_why_not_moreN_lab_accuracy,
                           Q19_why_not_moreN_test_profit_decis,
                           Q19_why_not_moreN_too_slow) %>% 
                           arrange(desc(percent))
#make a new column for names to use when graphing
Q19_why_not_moreN <- mutate(Q19_why_not_moreN,
                                        percent1 = round(percent*100,2),
                                        label_name = case_when(
                                          type == "Q19_why_not_moreN_cost" ~ "cost",
                                          type == "Q19_why_not_moreN_time" ~ "time",
                                          type == "Q19_why_not_moreN_lab_cost" ~ "cost of lab analysis",
                                          type == "Q19_why_not_moreN_variability" ~ "variability",
                                          type == "Q19_why_not_moreN_lab_accuracy" ~ "accuracy",
                                          type == "Q19_why_not_moreN_test_profit_decis" ~ "translate profitable decision",
                                          type == "Q19_why_not_moreN_too_slow" ~ "get results at right time") ) 

ggplot(Q19_why_not_moreN, aes(x = reorder(label_name, -percent), y = percent))+
  geom_col()+
  geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
  theme_classic()+
  labs(x= "reasons",
       y = "",
       title = "Please indicate why you don't do more SOIL Nitrogen testing:",
       subtitle = "Agronomist and grower",
       caption = "Please indicate why you don't do more SOIL Nitrogen testing:")+
  theme(axis.text.x=element_text(angle=45,hjust=1),
        plot.caption = element_text(size = 8, hjust = 0))+
   scale_y_continuous(labels = scales::percent, limits=c(0, 0.5))


```


#### **Question 20**
Please indicate why you don't do more SOIL Phosphorous testing

* The cost of soil sampling
* The time required for soil sampling
* The cost of soil testing lab analysis
* The difficulty in being able to represent the variability in a paddock
* The level of accuracy of soil testing lab analysis
* The ability to translate soil test results into a profitable fertiliser decision for my paddock
* Not being able to get soil test results at the right time for decision making
* General comments:


```{r Q20 agro and grower data work up and graph, echo=FALSE}



  
  
  Q20_why_not_moreP_cost <- data %>%
    group_by(  Q_20.1 ) %>%
    summarise(n = n()) %>%
    mutate(percent =(freq = n / sum(n)),
           type = "Q20_why_not_moreP_cost") %>% 
    filter( Q_20.1 != "NA") %>% 
    select(percent, type)
  
  Q20_why_not_moreP_time <- data %>%
    group_by(  Q_20.2 ) %>%
    summarise(n = n()) %>%
    mutate(percent =(freq = n / sum(n)),
           type = "Q20_why_not_moreP_time") %>% 
    filter( Q_20.2 != "NA") %>% 
    select(percent, type)
  
  Q20_why_not_moreP_lab_cost <- data %>%
    group_by(  Q_20.3 ) %>%
    summarise(n = n()) %>%
    mutate(percent =(freq = n / sum(n)),
           type = "Q20_why_not_moreP_lab_cost")%>% 
    filter( Q_20.3 != "NA") %>% 
    select(percent, type)
  
  Q20_why_not_moreP_variability <- data %>%
    group_by(  Q_20.4 ) %>%
    summarise(n = n()) %>%
    mutate(percent =(freq = n / sum(n)),
           type = "Q20_why_not_moreP_variability")%>% 
    filter( Q_20.4 != "NA") %>% 
    select(percent, type)
  
  Q20_why_not_moreP_lab_accuracy <- data %>%
    group_by(  Q_20.5) %>%
    summarise(n = n()) %>%
    mutate(percent =(freq = n / sum(n)),
           type = "Q20_why_not_moreP_lab_accuracy")%>% 
    filter( Q_20.5 != "NA") %>% 
    select(percent, type)
  
  Q20_why_not_moreP_test_profit_decis <- data %>%
    group_by( Q_20.6 ) %>%
    summarise(n = n()) %>%
    mutate(percent =(freq = n / sum(n)),
           type = "Q20_why_not_moreP_test_profit_decis")%>% 
    filter( Q_20.6 != "NA") %>% 
    select(percent, type)
  
  Q20_why_not_moreP_too_slow <- data %>%
    group_by(  Q_20.7 ) %>%
    summarise(n = n()) %>%
    mutate(percent =(freq = n / sum(n)),
           type = "Q20_why_not_moreP_too_slow") %>% 
    filter( Q_20.7 != "NA") %>% 
    select(percent, type)
  
  
  
  Q20_why_not_moreP <- rbind(Q20_why_not_moreP_cost,
                             Q20_why_not_moreP_time,
                             Q20_why_not_moreP_lab_cost,
                             Q20_why_not_moreP_variability,
                             Q20_why_not_moreP_lab_accuracy,
                             Q20_why_not_moreP_test_profit_decis,
                             Q20_why_not_moreP_too_slow)
Q20_why_not_moreP <- mutate(Q20_why_not_moreP,
                              percent1 = round(percent*100,2),
                              label_name = case_when(
                                type == "Q20_why_not_moreP_cost" ~ "cost",
                                type == "Q20_why_not_moreP_time" ~ "time",
                                type == "Q20_why_not_moreP_lab_cost" ~ "cost of lab analysis",
                                type == "Q20_why_not_moreP_variability" ~ "variability",
                                type == "Q20_why_not_moreP_lab_accuracy" ~ "accuracy",
                                type == "Q20_why_not_moreP_test_profit_decis" ~ "translate profitable decision",
                                type == "Q20_why_not_moreP_too_slow" ~ "get results at right time") ) 
  
  
  
  
  #head(Q17_why_not_moreP)
  ggplot(Q20_why_not_moreP, aes(x = reorder(label_name, -percent), y = percent))+
    geom_col()+
    geom_text(aes(label = percent(signif(percent),1), vjust = -1.0, hjust = 0.5))+
    theme_classic()+
    labs(x= "reasons",
         y = "",
         title = "Please indicate why you don't do more SOIL P testing:",
         subtitle = "Agronomist and growers",
         caption = "Please indicate why you don't do more SOIL Phosphorous testing")+
    theme(axis.text.x=element_text(angle=45,hjust=1),
          plot.caption = element_text(size = 8, hjust = 0))+
    scale_y_continuous(labels = scales::percent, limits=c(0, 0.5))
  
```
  
  

#### **Question 21** 

Please indicate if you agree/disagree with the following statements in relation to SOIL testing.

* My clients businesses would be more profitable if they did more soil testing than they do now
* Uncertainty about how the season will turn out makes it hard to get value from soil testing results
* My clients recommend the use of regular soil testing to other local farmers
* Feel free to comment on this response


#### **Question 22** 
On average, how much would your clients spend each year on soil testing (including sampling)?

#### **Question 23** 
Compared to five years' ago, has the amount of soil testing you do / recommend changed?

#### **Question 24** 
In five years' time, how much soil sampling do you expect to be doing / recommending?

# PLANT TESTING 

#### **Question 25**
How do you currently use plant testing?

#### **Question 26**
Please list the main 3 reasons you use plant testing data?

#### **Question 27**
Please indicate why you don't do more PLANT testing

* The cost of sampling
* The time required for sampling
* The cost of lab analysis
* The difficulty in being able to represent the variability in a paddock29
* The level of accuracy of lab analysis
* The ability to translate test results into a profitable decision
* Not being able to get test results at the right time for decision making
* General comments


#### **Question 28** 
Agronomist
Please indicate if you agree/disagree with the following statements in relation to PLANT testing

* My clients businesses would be more profitable if they did more plant testing than they do now
* Uncertainty about how the season will turn out makes it hard to get value from plant testing results
* My clients recommend the use of regular plant testing to other local farmers
* Feel free to comment on this response

Grower
Please indicate if you agree/disagree with the following statements in relation to  PLANT testing
* My farm business would be more profitable if I did more plant testing than I do now
* Uncertainty about how the season will turn out makes it hard to get value from plant testing results
* I would recommend the use of regular plant testing to other local farmers


#### **Question 29**
Agronomist
On average, how much would your clients spend per year on plant testing (including sampling)?
Grower
On average, how much would you spend per year on  plant testing (including sampling)?

#### **Question 30** 
Agronomist
Compared to five years' ago, has the amount of plant testing you do / recommend changed?
Grower
Compared to five years' ago, has the amount of plant testing you do on your farm changed?


#### **Question 31**
Agronomist
In five years' time,how much plant sampling do you expect to be doing / recommending?
Grower
In five years' time, how much plant sampling do you expect to be doing?


#### **Question 32**
Agronomist
Grower
Is the use of soil testing on your farm increasing your profitability?


#### **Question 33**
Agronomist
Grower
Please indicate why you don't do SOIL Nitrogen testing

The cost of soil sampling 
The level of accuracy of soil testing lab analysis
The ability to translate soil test results into a profitable fertiliser decision for my paddock
Not being able to get soil test results at the right time for decision making 
The time required for soil sampling 
The cost of soil testing lab analysis 
The difficulty in being able to represent the variability in a paddock 
General comments:


#### **Question 34**
Agronomist
Grower
Please indicate why you don't do SOIL Phosphorous  testing

The cost of soil sampling 
The level of accuracy of soil testing lab analysis
The ability to translate soil test results into a profitable fertiliser decision for my paddock
Not being able to get soil test results at the right time for decision making 
The time required for soil sampling 
The cost of soil testing lab analysis 
The difficulty in being able to represent the variability in a paddock 
General comments:


#### **Question 35** 
Agronomist
Grower
Please indicate if you agree/disagree with the following statements in relation to SOIL testing
* My farm business would be more profitable if I did more soil testing than I do now
* Uncertainty about how the season will turn out makes it hard to get value from soil testing results


#### **Question 36** 
Agronomist
Grower
Please indicate why you don't do any PLANT testing

* The cost of plant sampling
* The time required for plant sampling
* The cost of plant analysis
* The difficulty in being able to represent the variability in a paddock55
* The level of accuracy of plant analysis
* The ability to translate plant test results into a profitable fertiliser decision for my paddock
* Not being able to get plant test results at the right time for decision making
* Comment



#### **Question 37**
Agronomist
Please indicate if you agree/disagree with the following statements in relation to PLANT testing

* My clients businesses would be more profitable if they did more plant testing than they do now
* Uncertainty about how the season will turn out makes it hard to get value from plant testing results
* Feel free to comment on this response

Grower
Please indicate if you agree/disagree with the following statements in relation to  PLANT testing
* My farm business would be more profitable if I did more plant testing than I do now
* Uncertainty about how the season will turn out makes it hard to get value from plant testing results




#### **Question 38** 
What are the barriers to you undertaking...?

* Soil testing? - Sampling cost
* Soil testing? - Analysis cost
* Soil testing? - Sampling time
* Soil testing? - Analysis time
* Soil testing? - Understanding / interpreting results
* Soil testing? - Sampling method
* Plant testing? - Sampling cost
* Plant testing? - Analysis cost
* Plant testing? - Sampling time
* Plant testing? - Analysis time
* Plant testing? - Understanding / interpreting results
* Plant testing? - Sampling method
* Other (please specify)

#### **Question 40**
Please feel free to add any other comments or suggestions

#### **Question 41**
Grower
What information do you require to make better informed decisions regarding nutrient management?

#### **Question 42**
Grower
Where and how would you like to receive information regarding crop nutrition?

* Rural newspapers
* Farm consultants
* Workshops
* Merchandise companies
* Government agencies
* Field days
* Brochures / booklets
* Local trials
* Fertilizer company information, e.g. fact sheets
* Soil or plant testing companies
* Researchers
* Google
* Social media
* Other (please specify)


#### **Question 44**
How do you think researchers or the GRDC could assist you to get a better return on investment for your fertiliser decisions?


#### **Question 45**
Please feel free to add any other comments or suggestions



